\begin{abstract}

We describe a greedy heuristic route planning algorithm for finding time-optimised paths between two points in a graph, 
for electric vehicles (EVs). EVs will play an increasingly important role in the road traffic in the future. Due to the 
limited recharging possibilities and long recharging time of EVs the requirement for a different routing system emerges
in order to give the electric vehicles users a useful route plan. Unlike many of today's navigation systems, the greedy 
heuristic algorithm takes both the drive time and the recharge time into account. We further introduce a Linear Programming (LP) 
approach, which could be combined with the greedy heuristic algorithm and likely give a faster path at the cost of run 
time performance.

We compare the performance of the greedy heuristic algorithm with a naive algorithm on road
networks extracted from OpenStreetMap (OSM). We modify the OSM road network, so it contains Danish speed limits
and charging stations at variable positions and with varying charge rates. We compare the performance of the algorithms 
on four different parameters e.g. the distance to drive. 

\todo[inline]{HOW DID IT PERFORM?!}    

%We describe a greedy heuristic  algorithm for electric vehicles, this algorithm uses parameters about both the road network and the vehicle itself, to find a time efficient route plan between two points. We further introduce a linear programming method, which combined with the greedy-heuristic algorithm, can improve effectiveness and efficiency at the cost of computation time. Unlike the most common of today's navigation systems, the presented greedy-heuristic algorithm takes both the driving time and recharge time into account. This is a necessity as the recharging infrastructure is still limited, both in terms of the number of charge stations and their charge rates.\\


\end{abstract}