\section{Fastest Path}
Finding a shortest path from vertex $s$ to $t$ can easily be done with an algorithm such as Dijkstra's algorithm. But as we just showed in section \ref{sec:shorternotfaster} a shortest path does not necessarily imply a faster path. For the fastest path problem, we want to minimize the time it takes to travel from $s$ to $t$. However, the time it take to pass an edge cannot be pre-computed or generalized as charge rates of charge stations, consumption rates and the speed of the vehicle all change the time of an edge. All of these parameters dictates that there exist no optimal sub-structure to the problem. The topology of road networks also dictate that the triangle inequality will not always hold. An optimal solution asks for all simple paths to be solved independently, which is too complex to run on any country-sized road network in practice. The only approach is thus to change the problem or the procedure to a solution, where an optimal sub-structure exist and where the mathematical model of the road network is build to satisfy the triangle inequality as often as possible, resulting in minimal loss in path-time.\\

This section presents two approaches for solving the fastest path problem. Both of which is an expansion on Dijkstra's shortest path algorithm. Both use the greedy property of Dijkstra's, however the way we produce the time for edges is different for each approach. One uses a Greedy-Heuristic approach and the other uses a linear programming approach.